An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-10-30 mixedwindow.tex
Add new dummy macros for empirics
The empirics code defines some LaTeX macros that convey design
choices, etc. This commit provides default definitions for them
so that the LaTeX compiles whether or not the simulations have
been run. I've done this before, but must have missed these
macros.

\newcommand{\osum}[1]{\sum_{#1=R+1}^T}
\newcommand{\osumb}[1]{\sum_{#1=R'+1}^T}
\newcommand{\osumc}[1]{\sum_{#1=R+1}^{R'}}
\newcommand{\oavg}[1]{\tfrac{1}{P} \osum{#1}}
\newcommand{\oclt}[1]{\tfrac{1}{\sqrt{P}} \osum{#1}}
\newcommand{\ocltb}[1]{\tfrac{1}{\sqrt{P}} \osumb{#1}}
\newcommand{\ocltc}[1]{\tfrac{1}{\sqrt{P}} \osumc{#1}}

@@

\appendix
\section{Main theoretical results}
\label{sec:B}

\newcommand{\WesA}[1][]{\ocltb{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1}(F_t^{#1}) \osumb{t} (B_t^{#1} -
  B^{#1}) H_t^{#1}}
\newcommand{\WesC}[1][]{\ocltb{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}

@@

\begin{thm}
  If the conditions of Theorem~\ref{res:1} and that $y_{t+1} -
  x_t'\btrue$ is an MDS with respect to $\Fs_t$ then $\Sigmah_2 \to^p
  \Sigma$, where $\Sigmah_2 = \Sh_{ff} + \Sh_{2,fg} + \Sh_{2,fg}' +
  \Sh_{2,gg}$, with $\Sh_{ff}$ defined earlier and
  \begin{align}
    \Sh_{fg,2} &= \oavg{t} (\fh_t - \fb) (\gh_t - \gb_2)' \\
    \Sh_{gg,2} &= \oavg{t} (\gh_{2t} - \gb_2) (\gh_{2t} - \gb_2)' \\
    \gh_{2t} &= \Bigg\{\sum_{s=\max(t, R+1)}^T \tfrac1s \Fh_s \Bh_s\Bigg\} x_{t-1} \ep_t
    \intertext{and}
    \gb_2 &= \oavg{t} \gh_{2t}.
  \end{align}
\end{thm}

\section{Supporting results}

\begin{lema}\label{res:a1}
  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$. Then
  \begin{equation*}
    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
  \end{equation*}
\end{lema}

\begin{proof}
  We can rewrite this summation as
  \begin{multline*}
    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
    \ocltc{t} 2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue)
    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
  \end{multline*}
  Each of these individual summations can be shown to converge to
  zero in probability. First,
  \begin{equation*}
    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
    = O(R'/\sqrt{P}).
  \end{equation*}
  Also,
  \begin{align*}
    \Big\lvert \ocltc{t} &2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
    &\leq \ocltc{t} 2 \big\lvert (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t' \big\rvert
    \max_{t=R+1,\dots,R'} \lvert  \bh_t - \btrue \rvert \\
    & = O_p(R'/\sqrt{P})
  \end{align*}
  and
  \begin{equation*}
    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
    \leq \ocltc{t} \lvert x_t'x_t \rvert \max_{t=R+1,\dots,R'} (\bh_t - \btrue)'(\bh_t - \btrue)
    = O_p(R'/\sqrt{P}).
  \end{equation*}
  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
  construction, this completes the proof.
\end{proof}

\begin{lema}\label{res:a2}
  Suppose $a \in [0,\frac12)$ and Assumptions~\ref{a1} -- \ref{a4}
  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
  \infty$ and $R' = o(\sqrt{P})$. Then
  \begin{enumerate}
  \item $\sup_{t=R'+1,\dots,T} | t^a H_t | \to^p 0$.
  \item $\sup_{t=R+1,\dots,R'} | t^a H_t | = O_p(1)$.
  \item $\sup_{t = R'+1,\dots,T} | t^a(\bh_t - \btrue) | \to^{p} 0$.
  \item $\sup_{t = R+1,\dots,R'} | t^a(\bh_t - \btrue) | = O_p(1)$.
  \end{enumerate}
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a2}]
  We will prove each part in order.
  \begin{enumerate}
  \item The process $x_{t-1} \ep_t$ is $L_2$-NED of size $-1/2$ (on
    the same mixing process as the original variables) by
    Assumption~\ref{a3}, and the moment and size conditions in that
    assumption make it an $L_2$-mixingale of size $-1/2$ as well. The
    mixingale \fclt\ implies that, for any $t \to \infty$ as $T \to \infty$,
    \begin{equation}\label{eq:2}
      t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \to^d \lim (T^{1/2} / t^{1-a}) \cdot W(\lim t/T)
    \end{equation}
    where $W(\cdot)$ is a multivariate Gaussian process.

    If $t/T \to \gamma$ then $T^{1/2} / t^{1-a} \to 0$ and the limit
    in~\eqref{eq:2} is almost surely 0. If $t/T \to 0$, then
    \begin{equation*}
      \E\Big( t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big)^2 = t^{2a - 1}\, O(1)
    \end{equation*}
    and the limit in~\eqref{eq:2} is again almost surely 0. The
    Continuous Mapping Theorem then implies that
    \begin{equation*}
      \sup_{t=R'+1,\dots,T} \Big| t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big| \to^p 0.
    \end{equation*}
  \item Again, $x_{t-1} \ep_t$ is an $L_2$-mixingale of size
    $-1/2$. As a result, we can use a maximal inequality of
    \cite{Mcl:75} (also available as Corollary 16.10 in
    \citealp{Dav:94}), giving
    \begin{align*}
      \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s\Big)^2 \Big\rvert
      &\leq \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(\sum_{s=2}^t s^{a-1} x_{s-1} \ep_s\Big)^2 \Big\rvert \\
      &= O(1) \sum_{s=2}^{R'} s^{2a - 2}
    \end{align*}
    which converges to a finite limit.
  \item We have
    \begin{multline*}
      \sup_{t=R'+1,\dots,T} | t^a (\hat{\beta}_t - \btrue) | \leq \\
      \sup_{t,u =R'+1,\dots,T} \Big| [ \hat{B}_u - B]
      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R'+1,\dots,T} \Big|
      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|
    \end{multline*}
    and both terms converge to zero in probability by Part 1 and by
    assumption.
  \item Similar to the previous argument, we have
    \begin{multline*}
      \sup_{t=R+1,\dots,R'} | t^a (\hat{\beta}_t - \btrue) | \leq \\
      \sup_{t,u =R+1,\dots,R'} \Big| [ \hat{B}_u - B]
      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R+1,\dots,R'} \Big|
      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|.
    \end{multline*}
    Both terms are $O_p(1)$ by Part 2 and by assumption. \qedhere
  \end{enumerate}
\end{proof}

@@

\begin{proof}[Proof of Lemma~\ref{res:a4}]
We can write
\begin{equation*}
  \Big\lvert \WesA \Big\rvert \leq
  \Big\lvert \ocltb{t} (F_t - \E F_t) B \Big\rvert
  \sup_{t = R'+1,\dots,T} | H_t |.
\end{equation*}
From Lemma~\ref{res:a2}, $\sup_{t = R'+1,\dots,T} | H_t | \to^p 0$. The \clt\ implies
that $\ocltb{t} (F_t - \E F_t) = O_p(1)$,
establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
and~\eqref{eq:13} are similar.
\end{proof}

>>>>

\newcommand{\osum}[1]{\sum_{#1=R+1}^T}
\newcommand{\oavg}[1]{\tfrac{1}{P} \osum{#1}}
\newcommand{\oclt}[1]{\tfrac{1}{\sqrt{P}} \osum{#1}}

@@

\appendix
\section{Proofs of Main Theoretical Results}
\label{sec:B}

\newcommand{\WesA}[1][]{\oclt{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1} F_t^{#1} \osum{t} (B_t^{#1} -
  B^{#1}) H_t^{#1}}
\newcommand{\WesC}[1][]{\oclt{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}

@@

\section{Supporting Results}

\begin{lema}\label{res:a2}
  Suppose $a \in [0,\frac12)$ and the conditions of Theorem~\ref{res:3}
  hold.
  \begin{enumerate}
  \item $P^a \sup_t | H_{t} | \to^p 0$.
  \item $P^a \sup_t | \bh_{t} - \btrue | \to^{p} 0$.
  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t) = O_{p}(1)$.
  \end{enumerate}
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a2}]
  \begin{enumerate}
  \item The process $\tfrac{1}{\sqrt{T}} h_{s}$ satisfies
    \citepos[Theorem 3.1]{JoD:00b} functional \clt.  So
    \begin{equation}
      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s} \Big| =
      P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Big| \to^{p} 0
    \end{equation}
    with the convergence following from the continuous mapping
    theorem.
  \item We have
    \begin{equation}
      P^a \sup_t | \bh_t - \btrue | = P^a \sup_t |\Bh_{t}
      H_{t}| \leq \sup_{t,u} \Big| [ \Bh_u - B]
      \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t} \Big|
      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
    \end{equation}
    and both terms converge to zero in (conditional) probability by
    the previous argument and by assumption.
  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t)$ obeys
    \citepos{Jon:97} \clt, so the result is trivial.
  \end{enumerate}
\end{proof}

@@

\begin{proof}[Proof of Lemma~\ref{res:a4}]
We can write
\begin{equation*}
  \Big\lvert \WesA \Big\rvert \leq 
  \Big\lvert \oclt{t} (F_t - \E F_t) B \Big\rvert
  \sup_t | H_t |.
\end{equation*}
From Lemma~\ref{res:a2}, $\sup_t | H_t | \to^p 0$ and $\oclt{t}
(F_t - \E F_t) = O_p(1)$, establishing~\eqref{eq:11}. The proofs
of \eqref{eq:12} and \eqref{eq:13} are similar.
\end{proof}
